---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw4 - Simple Linear Regression Package

<!-- badges: start -->
[![R-CMD-check](https://github.com/yunzhang77/hw4/workflows/R-CMD-check/badge.svg)](https://github.com/yunzhang77/hw4/actions)
[![codecov](https://codecov.io/gh/yunzhang77/hw4/branch/master/graph/badge.svg?token=qhHpcXtRu7)](https://codecov.io/gh/yunzhang77/hw4)
<!-- badges: end -->

The goal of this R package is to perform simple linear regression analysis with a single explanatory variable. This package can calculate intercept and slope for the regression model, perform statistical testing on the regression (T-test and F-test), calculate R-squared and adjusted R-squares, and plot linear regression line. This package also utilize S3 generic method/function to provide user-friendly display of results. 

## Installation

You can install the development version of hw4 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("yunzhang77/hw4")
```

## Quick Guide

After the package is installed on your local R environment, you can perform simple linear regression analysis by calling:
  - `linear_regression()`: which will take three arguments - independent variable name, dependent variable name, and data frame
  - `plot_linear_regression()`: which will take two arguments - result from `linear_regression()` and data frame
  - `print()` can be called to print user-friendly linear regression result that contains regression coefficients
  - `summary()` can be called to print statistics of the regression model 
To better help user to learn this package, two example data sets are included in the package `data_glucose_simple` and `happiness_data`. `data_glucose_simple` can be used to test the functionality of the package and `happiness_data` is a relatively more challening data sets that could be used to validate package performance. See example below to see how to use this package. 

## Example

This is a basic example which shows you how to use this package solve simple linear regression problem:

```{r example}
library(hw4)

# perform regression analysis
result <- linear_regression("income", "happiness", happiness_data)

# print regression coefficient and statistics analysis on the regression model
print(result)
summary(result)
```

You can also generate linear regression plots on the result, for example:

```{r pressure, echo = FALSE}
plot_linear_regression(result, happiness_data)
```

The red line indicates the fitted linear regression line, whereas black dots represent original data points. For more specific help on each function, type `?function_name` on the RStudio console. 

## Need Help?

If you encounter a problem/bug, please feel free to report on the GitHub page. :) 
